---
title: "ms amenazas"
author: "Pablo Cortes"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
    toc_depth: '3'
    number_sections: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
    number_sections: yes
---

```{r, echo=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE,error=FALSE)
```

```{r}
library(readxl)
library(tidyverse) 
library(gridExtra) 
library(bibliometrix)
library(tools) 
library(ggpubr)
library(DT)
library(igraph)
library(quanteda)
library(quanteda.textplots)
library(stm)
library(topicmodels)
library(tidytext)

```

```{r}

data <- read_excel("CC_2021-08-24.xlsx")

data<-data %>% 
  filter(Utilidad == "Y")
```

# Table 1. Main information

```{r}
#Generamos database_bibliometrix ue solo incluye Metadatos (eliminamos las primeras dos columnas)
data_bibliometrix<-data[,10:63]
```

```{r}
# Aplicamos un análisis bibliométrico con bibliometrix
results<- biblioAnalysis(data_bibliometrix, sep=";")
```

```{r,results='hide'}
summary(results, k=10, pause=F, width=130)
```

```{r}
main_information <- data.frame(Description=c("Timespan", "Documents", "Sources",
"Authors", "Authors of single-authored documents","Authors of multi-authored documents", "Single-authored documents","Keywords-Plus", "Author's Keywords"),
                 Counts=c("1966-2021","1569", "642",
"4844", "95","4749", "106","5861", "4402"))

datatable(main_information, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=10))
```


# Figure 2. Annual number of publications

```{r}
conteo<-data%>%
    count(PY)%>%
    mutate(cumulative=cumsum(n)) %>%
    mutate(percentage=100*(n / sum(n)))%>%
    mutate(percentage_cum=100*(cumulative / sum(n))) %>% 
    mutate(across(where(is.numeric), round, 2))
```

```{r,results='hide'}
### Generamos el objeto conteo_ascendente_year con cálculos a utilizar en la sección resultados

conteo_ascendente_year<-conteo %>% 
            arrange(percentage_cum)

datatable(conteo_ascendente_year, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=15))

```

```{r,results='hide'}
### Generamos el objeto conteo_ascendente_n con cálculos a utilizar en la sección resultados
conteo_ascendente_n<-conteo %>% 
  arrange(n)
datatable(conteo_ascendente_n, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=15))

```

```{r,fig.height=5, fig.width=10}
TrendLine1<-ggplot(conteo, aes(x = PY, y = n))+
	geom_line(colour="#333333", size=1)+
    geom_point(aes(x = PY, y = n), colour="#333333",size =4) +
	scale_x_continuous(breaks=c(1960,1965,1970,1975,1980,1985,1990,1995,2000,2005,2010,2015, 2021),limits=c(1965, 2021))+
                       scale_y_continuous(breaks=c(0,20,40,60,80,100,120,140,160,180,200,220,240),limits=c(0,240))+
    xlab("Year") + ylab("Number of publications")+
  theme(axis.text =element_text(size=16,color="#13100D"),
        axis.title=element_text(size=23,color="#13100D"),
        panel.background = element_blank(),
        panel.border = element_rect(color="#13100D", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))

TrendLine1

```

# Figure 3. Top 10 publishing journals
```{r}
Source<-as.data.frame(results$Sources)
```

```{r, results='hide'}
Top_Ten<-Source %>% 
  mutate(Source = str_to_title(SO)) %>% #Convertir a title case
  arrange(-Freq) %>% 
  filter(Freq > 14)
datatable(Top_Ten, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=10))
```

```{r,fig.height=5, fig.width=8}
ggdotchart(Top_Ten, x = "Source", y = "Freq",
           sorting = "descending",                       
           add = "segments",                             
           rotate = TRUE,                                
           dot.size = 10,                                
           label = Top_Ten$Freq,                        
           font.label = list(color = "white", size = 11, vjust = 0.5),               
           ggtheme = theme_pubr())+                      

     xlab("") + ylab("Number of publications")+
    scale_y_continuous(breaks=c(0,10,20,30,40,50),limits=c(0, 52))+
    theme(axis.text =element_text(size=13,color="#191919"),
        axis.title=element_text(size=20,color="#191919"),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))
```

# Figure 4. Top 10 affiliations

```{r}
Institutions<-as.data.frame(results$Affiliations)
```

```{r}
#Exportando la base de datos
#library(tibble)
#inst<-as_tibble(Institutions)
#write.table(inst,"Institutions.txt",sep="\t")
#data_Institutions <- read_excel("Institutions.xlsx")
```

```{r, results='hide'}
Top_Ten<-Institutions %>% 
  mutate(Affiliation = str_to_title(AFF)) %>% #Convertir a title case
  arrange(-Freq) %>% 
  filter(Freq > 70)
datatable(Top_Ten, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=10))
```

```{r,fig.height=5, fig.width=8}
ggdotchart(Top_Ten, x = "Affiliation", y = "Freq",
           sorting = "descending",                       
           add = "segments",                             
           rotate = TRUE,                                
           dot.size = 10,                                
           label = Top_Ten$Freq,                        
           font.label = list(color = "white", size = 11, vjust = 0.5),               
           ggtheme = theme_pubr())+                      

     xlab("") + ylab("Number of publications")+
    scale_y_continuous(breaks=c(0,100,200,300,400,500),limits=c(0, 550))+
    theme(axis.text =element_text(size=13,color="#191919"),
        axis.title=element_text(size=20,color="#191919"),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))
```

# Figure 5. Top 13 productive authors

```{r}
Authors<-as.data.frame(results$Authors)
```

```{r}
#Exportando la base de datos
#aut<-as_tibble(Authors)
#write.table(aut,"Authors",sep="\t")
#data_Authors <- read_excel("Authors.xlsx")
#
#MORENO PI -->MORENO P
#GARREAUD RA-->GARREAUD R
#CAVIERES LA -->CAVIERES L
```



```{r, results='hide'}
Top_Ten<-Authors %>% 
  mutate(Author = str_to_title(AU)) %>% #Convertir a title case
  arrange(-Freq) %>% 
  filter(Freq > 14)
datatable(Top_Ten, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=13))
```

```{r,fig.height=5, fig.width=8}
ggdotchart(Top_Ten, x = "Author", y = "Freq",
          sorting = "descending",                       
           add = "segments",                             
           rotate = TRUE,                                
           dot.size = 10,                                
           label = Top_Ten$Freq,                        
           font.label = list(color = "white", size = 11, vjust = 0.5),               
           ggtheme = theme_pubr())+                      

     xlab("") + ylab("Number of publications")+
    scale_y_continuous(breaks=c(0,10,20,30),limits=c(0,35))+
    theme(axis.text =element_text(size=13,color="#191919"),
        axis.title=element_text(size=20,color="#191919"),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))
```




# Figure 6. Top 10 most relevant author´s keywords over period 1990-2021.

# Figure 7. Top 20 most relevant words based on publishes abstracts. A = 1990-1999, B = 2000-2009, C = 2010-2021 and D = 1990-2021.

```{r}
data_1999<-data %>% 
filter(PY< 2000)

data_2009<-data%>%
filter(PY>1999 & PY< 2010)

data_2021<-data %>% 
filter(PY> 2009)
```

```{r, warning=FALSE}
corpus_abstract <- corpus(data$AB, docnames = data$doc_id, docvars = data.frame(year = data$PY))
corpus_abstract_1999 <- corpus(data_1999$AB, docnames = data_1999$doc_id, docvars = data.frame(year = data_1999$PY))
corpus_abstract_2009 <- corpus(data_2009$AB, docnames = data_2009$doc_id, docvars = data.frame(year = data_2009$PY))
corpus_abstract_2021 <- corpus(data_2021$AB, docnames = data_2021$doc_id, docvars = data.frame(year = data_2021$PY))
```

```{r, warning=FALSE}
list_stopwords <- readLines("list_stopwords.csv", encoding = "UTF-8")
other_stopwords<- c("elsevier","b.v","rights"," reserved","-1","-2","yr","study","b.p","bp")
original_word<-c("sp","glacier","southern")
new_word<-c("species","glaciers","south")

```

```{r}
toks_all <- corpus_abstract %>%
    tokens(remove_punct = TRUE,remove_numbers = TRUE, remove_symbols = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("english")) %>% 
    tokens_select(c(-1,list_stopwords,other_stopwords), selection = "remove", padding = FALSE) %>% 
    tokens_replace(pattern=original_word, 
                  replacement=new_word)

  toks_1999 <- corpus_abstract_1999 %>%
    tokens(remove_punct = TRUE,remove_numbers = TRUE, remove_symbols = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("english")) %>% 
   tokens_select(c(-1,list_stopwords,other_stopwords), selection = "remove", padding = FALSE) %>% 
    tokens_replace(pattern=original_word, 
                  replacement=new_word)

toks_2009 <- corpus_abstract_2009 %>%
    tokens(remove_punct = TRUE,remove_numbers = TRUE, remove_symbols = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("english")) %>% 
    tokens_select(c(-1,list_stopwords,other_stopwords), selection = "remove", padding = FALSE) %>% 
    tokens_replace(pattern=original_word, 
                  replacement=new_word)

toks_2021 <- corpus_abstract_2021 %>%
    tokens(remove_punct = TRUE,remove_numbers = TRUE, remove_symbols = TRUE) %>%
    tokens_tolower() %>%
    tokens_remove(stopwords("english")) %>% 
    tokens_select(c(-1,list_stopwords,other_stopwords), selection = "remove", padding = FALSE) %>% 
    tokens_replace(pattern=original_word, 
                  replacement=new_word)
```

```{r}
wfreq_all <- toks_all %>%
  unlist()%>% 
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  head(20) %>%
  rename("unigram 1990-2021"= 1,frequency = 2)


wfreq_1999 <- toks_1999 %>%
  unlist()%>% 
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  head(20) %>%
  rename("unigram 1990-1999" = 1,frequency = 2)

wfreq_2009 <- toks_2009 %>%
  unlist()%>% 
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  head(20) %>%
  rename("unigram 2000-2009" = 1,frequency = 2)

wfreq_2021 <- toks_2021 %>%
  unlist()%>% 
  table() %>%
  as.data.frame() %>%
  arrange(desc(Freq)) %>%
  head(20) %>%
  rename("unigram 2010-2021" = 1,frequency = 2)

```

```{r, results='hide'}
wfreq<-cbind(wfreq_1999,wfreq_2009,wfreq_2021,wfreq_all)
datatable(wfreq, class = 'cell-border stripe',
          options = list(searching=FALSE, pageLength=20))

```

```{r}
hist_1999<-wfreq_1999 %>%
  rename(unigram="unigram 1990-1999") %>% 
  ggplot(aes(x = reorder(unigram, -frequency, mean), y = frequency)) +
  geom_bar(stat = "identity") +
  labs(title=NULL,x=NULL, y=NULL)+
  theme(axis.text =element_text(size=12,color="#191919"),
        axis.text.x = element_text(angle = 45,hjust = 1),
        axis.title=element_text(size=20,color="#191919"),
        plot.title = element_text(color="#191919", hjust=0),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))

hist_2009<-wfreq_2009 %>%
  rename(unigram="unigram 2000-2009") %>% 
  ggplot(aes(x = reorder(unigram, -frequency, mean), y = frequency)) +
  geom_bar(stat = "identity") +
  labs(title=NULL,x=NULL, y=NULL)+
  theme(axis.text =element_text(size=12,color="#191919"),
        axis.text.x = element_text(angle = 45,hjust = 1),
        axis.title=element_text(size=20,color="#191919"),
        plot.title = element_text(color="#191919", hjust=0),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))

hist_2021<-wfreq_2021 %>%
  rename(unigram="unigram 2010-2021") %>% 
  ggplot(aes(x = reorder(unigram, -frequency, mean), y = frequency)) +
  geom_bar(stat = "identity") +
  labs(title=NULL,x=NULL, y=NULL)+
  theme(axis.text =element_text(size=12,color="#191919"),
        axis.text.x = element_text(angle = 45,hjust = 1),
        axis.title=element_text(size=20,color="#191919"),
        plot.title = element_text(color="#191919", hjust=0),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))

hist_all<-wfreq_all %>%
  rename(unigram="unigram 1990-2021") %>% 
  ggplot(aes(x = reorder(unigram, -frequency, mean), y = frequency)) +
  geom_bar(stat = "identity") +
labs(title=NULL,x=NULL, y=NULL)+
  theme(axis.text =element_text(size=12,color="#191919"),
        axis.text.x = element_text(angle = 45,hjust = 1),
        axis.title=element_text(size=20,color="#191919"),
        plot.title = element_text(color="#191919", hjust=0),
        panel.background = element_blank(),
        panel.border = element_rect(color="#191919", size=1, fill=NA),
        panel.grid.major =  element_line(colour = "#708090",size=0.1))
```

```{r,fig.height=10, fig.width=9}
figure <- ggarrange(hist_1999,hist_2009,hist_2021,hist_all,
                    labels = c("A", "B","C","D"),
                    ncol = 2, nrow = 2,
                      heights = c(0.5, 0.5))
annotate_figure(figure,
                left = text_grob("Frequency", color = "#191919", rot = 90, size=20))

```

# Table 2. Top 20 most relevant bigrams based on publishes abstracts over period 1990-2021.
```{r}
toks_bigram<- toks_all %>%
  unlist()

word_bigrams_all <- data.frame(toks_bigram[1:length(toks_bigram)-1], 
                       toks_bigram[2:length(toks_bigram)]) %>%
  rename(Word1 = 1,
                Word2 = 2) %>%
  mutate(Bigram = paste0(Word1, " ", Word2)) %>%
  group_by(Bigram) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>% 
  head(20)%>%
  rename("bigram 1990-2021" = 1,frequency = 2)

toks_bigram_1999 <- toks_1999 %>%
  unlist()

word_bigrams_1999 <- data.frame(toks_bigram_1999[1:length(toks_bigram_1999)-1], 
                       toks_bigram_1999[2:length(toks_bigram_1999)]) %>%
  rename(Word1 = 1,
                Word2 = 2) %>%
  mutate(Bigram = paste0(Word1, " ", Word2)) %>%
  group_by(Bigram) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>% 
  head(20)%>%
  rename("bigram 1990-1999" = 1,frequency = 2)

toks_bigram_2009 <- toks_2009 %>%
  unlist()

word_bigrams_2009 <- data.frame(toks_bigram_2009[1:length(toks_bigram_2009)-1], 
                       toks_bigram_2009[2:length(toks_bigram_2009)]) %>%
  rename(Word1 = 1,
                Word2 = 2) %>%
  mutate(Bigram = paste0(Word1, " ", Word2)) %>%
  group_by(Bigram) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>% 
  head(20)%>%
  rename("bigram 2000-2009" = 1,frequency = 2)

toks_bigram_2021 <- toks_2021%>%
  unlist()
word_bigrams_2021 <- data.frame(toks_bigram_2021[1:length(toks_bigram_2021)-1], 
                       toks_bigram_2021[2:length(toks_bigram_2021)]) %>%
  rename(Word1 = 1,
                Word2 = 2) %>%
  mutate(Bigram = paste0(Word1, " ", Word2)) %>%
  group_by(Bigram) %>%
  summarise(Frequency = n()) %>%
  arrange(-Frequency) %>% 
  head(20)%>%
  rename("bigram 2010-2021" = 1,frequency = 2)

```

```{r}
bigramfreq<-cbind(word_bigrams_1999,word_bigrams_2009,word_bigrams_2021,word_bigrams_all)

datatable(bigramfreq, class = 'cell-border stripe',
          options = list(pageLength=20))

```


## Table 3. Selective bigrams from abstracts

### cliamte change
```{r}
unigram_context<-kwic(toks_all, pattern=phrase("climate change"), 5)
  

datatable(unigram_context, class = 'cell-border stripe',
          options = list(pageLength=20))

```



### methane
```{r}
unigram_context<-kwic(toks_all, pattern=phrase("methane"), 5)
  

datatable(unigram_context, class = 'cell-border stripe',
          options = list(pageLength=20))

```


# Figure 9. Words co-ocurrence network based on publishes abstracts. A = 1990-1999, B = 2000-2009, C = 2010-2021 and D = 1990-2021.

```{r}
fcmat_all <- fcm(toks_all, context = "window", tri = FALSE)
feat_all <- names(topfeatures(fcmat_all, 20, decreasing = TRUE))
fcm_20_all<-fcm_select(fcmat_all, pattern = feat_all)

fcmat_1999 <- fcm(toks_1999, context = "window", tri = FALSE)
feat_1999 <- names(topfeatures(fcmat_1999, 20, decreasing = TRUE))
fcm_20_1999<-fcm_select(fcmat_1999, pattern = feat_1999)

fcmat_2009 <- fcm(toks_2009, context = "window", tri = FALSE)
feat_2009 <- names(topfeatures(fcmat_2009, 20, decreasing = TRUE))
fcm_20_2009<-fcm_select(fcmat_2009, pattern = feat_2009)


fcmat_2021 <- fcm(toks_2021, context = "window", tri = FALSE)
feat_2021 <- names(topfeatures(fcmat_2021, 20, decreasing = TRUE))
fcm_20_2021<-fcm_select(fcmat_2021, pattern = feat_2021)

```


```{r}
co_net_1999<-textplot_network(fcm_20_1999,min_freq = 0.5,
                 edge_color="#333333",
                 edge_alpha=0.25,
                 vertex_color="#191919",
                 vertex_labelcolor="#191919",
                 vertex_labelsize = 3.5,
                 vertex_size = (rowSums(fcm_20_1999)/min(rowSums(fcm_20_1999)))/3)

co_net_2009<-textplot_network(fcm_20_2009,min_freq = 0.5,
                 edge_color="#333333",
                 edge_alpha=0.25,
                 vertex_color="#191919",
                 vertex_labelcolor="#191919",
                 vertex_labelsize = 3.5,
                 vertex_size = (rowSums(fcm_20_2009)/min(rowSums(fcm_20_2009)))-0.5)

co_net_2021<-textplot_network(fcm_20_2021,min_freq = 0.5,
                 edge_color="#333333",
                 edge_alpha=0.25,
                 vertex_color="#191919",
                 vertex_labelcolor="#191919",
                 vertex_labelsize = 3.5,
                 vertex_size = 1.2*rowSums(fcm_20_2021)/min(rowSums(fcm_20_2021)))

co_net_all<-textplot_network(fcm_20_all,min_freq = 0.5,
                 edge_color="#333333",
                 edge_alpha=0.25,
                 vertex_color="#191919",
                 vertex_labelcolor="#191919",
                 vertex_labelsize = 3.5,
                 vertex_size = 1.2*rowSums(fcm_20_all)/min(rowSums(fcm_20_all)))

figure <- ggarrange(co_net_1999,co_net_2009,co_net_2021,co_net_all,
                    labels = c("A", "B","C","D"),
                    ncol = 2, nrow = 2)

figure             
```

# Table 4.Top ten terms per topic from latent Dirichlet allocation modeling.

```{r}
#https://www.r-bloggers.com/2019/10/advancing-text-mining-with-r-and-quanteda-2/

dfm_word<-dfm(toks_all, tolower = FALSE)

mydfm.un.trim <-
  dfm_trim(
    dfm_word,
    min_docfreq = 0.075,
    # min 7.5%
    max_docfreq = 0.90,
    # max 90%
    docfreq_type = "prop"
  ) 

# Convert the trimmed DFM to a topicmodels object
dfm2topicmodels <- convert(mydfm.un.trim, to = "topicmodels")

#Set parameters for Gibbs sampling
burnin <- 4000
iter <- 2000
thin <- 500
seed <-list(2003,5,63,100001,765)
nstart <- 5
best <- TRUE

#Number of topics
k <- 5

lda.model <- LDA(dfm2topicmodels,k, method="Gibbs", control=list(nstart=nstart, seed = seed, best=best, burnin = burnin, iter = iter, thin=thin))
```

```{r}
topics_dla<-tidy(lda.model, matrix="beta")
 
#per-topic-per-word probabilities, called β (“beta”).  the model computes the probability of that term being generated from that topic. 
```

```{r}
top_topics_dla <- topics_dla %>% 
  group_by(topic) %>%
  slice_max(beta, n = 10) %>% 
  ungroup() %>%
  arrange(topic, -beta)
datatable(top_topics_dla, class = 'cell-border stripe',
          options = list(pageLength=10))
```


```{r}
top_topics_dla  %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free",ncol=2) +
  scale_y_reordered()
```



```{r,results='hide'}
#Find probabilities associated with each topic assignment
topicProbabilities <- as.data.frame(lda.model@gamma[1:15,]) 
topicTerms<-as.data.frame(terms(lda.model, 15))
topic<-cbind(topicTerms,topicProbabilities)
```
```{r, results='hide'}
df1<-topicTerms
df2<-topicProbabilities
tot_cols <- ncol(df1) + ncol(df2)
tot_rows <- nrow(df1) + nrow(df2)

# Create empty output data.frame with desired number of rows and cols
df <- data.frame(matrix(ncol=tot_cols, nrow=tot_rows))

# Assign columns to output data.frame
df[, c(seq(1, tot_cols, 2))] <- df1
df[, seq(2, tot_cols, 2)] <- df2

# Assign columns to output data.frame
colnames(df) <- c(rbind(colnames(df1), colnames(df2)))

datatable(df, class = 'cell-border stripe',
          options = list(pageLength=15))
```

